---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


<!-- badges: start -->
  [![R-CMD-check](https://github.com/ylzzzzz/linearregression/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ylzzzzz/linearregression/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/ylzzzzz/linearregression/graph/badge.svg)](https://app.codecov.io/gh/ylzzzzz/linearregression)
<!-- badges: end -->


## Overview


`linearregression` provides a toy implementation of
ordinary least squares (OLS) using the normal equations.

- `toy_lm()` accepts a model formula and a data frame, checks that all predictors are numeric, fits the OLS model using `β̂ = (XᵀX)⁻¹ Xᵀy `and returns a full coefficient table (estimates, standard errors, t‐statistics, and p‐values).

- Additional statistics returned include fitted values, residuals, mean squared error (MSE),
  residual standard error (RSE), R², adjusted R², and the overall F‐test (statistic, degrees of freedom, and p‐value).


## Installation

You can install the development version of linearregression from GitHub with:

```{r, eval = FALSE}
devtools::install_github(
  "ylzzzzz/linearregression",
  build_vignettes = TRUE
)

```

## Usage: 


```{r, message = FALSE}
library(linearregression)

# Fit a model
fit <- toy_lm(mpg ~ wt + hp + disp, data = mtcars)

# View the coefficient table
fit$coefficients

# Additional model statistics
fit$r.squared        # R-squared
fit$adj.r.squared    # Adjusted R-squared
fit$f.statistic      # F-statistic for overall significance
fit$f.pvalue         # p-value for the F-test
```

More detailed tutorials can be found in the vignettes.

```{r, eval = FALSE}
browseVignettes("linearregression")
```

## Getting help

If you encounter a bug or have suggestions for improvement, please open an issue on  
[GitHub](https://github.com/ylzzzzz/linearregression/issues).

