---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(linearregression)
```

# Introduction

This vignette provides a step-by-step demonstration of how to use the `linearregression` package.  
We’ll fit a multiple linear regression model using the classic `mtcars` dataset, interpret the output, and discuss potential corner cases such as collinearity.

# Example: Fitting a Linear Model

```{r example}
# Load dataset
data(mtcars)

# Fit model using toy_lm() 
fit_toy <- toy_lm(mpg ~ wt + hp + disp, data = mtcars)

# Display results
fit_toy
```

# Comparing Results with R's Built-in `lm()`

To check that `toy_lm()` works correctly, we can compare its results with R’s built-in `lm()` function using the same predictors and dataset:

```{r compare_lm}
# Fit model using lm
fit_lm <- lm(mpg ~ wt + hp + disp, data = mtcars)

# Display results of lm
summary(fit_lm)
```
